The \project{unRAVE} catalog

### 2016-09-02 article/unrave.tex
De-scoped some aspects: photometry in pixels; censoring; fit velocity at test time; priors on test labels

\begin{document}
% Remove at submission:
\slugcomment{{\color{red} \textbf{To appear on arXiv on 9 September 2016 (\difftoday{2016}{9}{7}away)}}}

@@

% Stubs for discussion & analysis.
% TODO: Inserting 2MASS photometry as fake pixels
% TODO: Censoring masks on abundance labels
% TODO: Priors on astrophysical parameters from isochrones
% TODO: Include velocities and rotational velocities at test time?

@@

\noindent{}where $\Lambda$ is a regularization parameter which we will heuristically set
for each model in later sections, and $Q(\vectheta)$ is a regularizing function that 
encourages $\vectheta$ values to take on zero values without breaking convexity:
\begin{eqnarray}\label{eq:regularization-function}
	Q(\vectheta) = \sum_{d=1}^{D-1} |{\theta_d}|
\end{eqnarray}

@@

The \rave\ survey performed repeat observations for 23,288 stars  with time 
intervals ranging from a few hours to up to four years.  This timing was 
constructed to be quasi-logarithmic such that spectroscopic binaries could
be optimally identified. Most of the stars that were observed multiple times
were only observed twice, with thirteen visits being the maximum number 
of observations for any target.  These repeat observations allow us to 
quantify the level of (in)correctness in our formal errors.  For every star
with multiple visits we constructed a high S/N stacked spectrum for that
star, weighted by the inverse variances in the individual visit spectra,
which then served as the basis of comparison to all individual visits.  
Figure \ref{fig:formal-errors-comparison} shows the difference in labels 
between the comparison spectrum and a repeat visit, normalized by their 
formal errors summed in quadrature (e.g., 
$\Delta\logg/\sqrt{\sigma_{\logg,stacked}^2 + \sigma_{\logg,visit}^2}$).
If our measurements were unbiased by S/N and the errors were representative, 
these values should be normally distributed with a zero mean and unit variance.
\stub{Are they? Should we inflate our formal errors?}

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/ges-comparison.png}
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{Gaia-ESO Survey} fourth internal data release.\label{fig:ges-dr4-comparison}}
\end{figure*}

>>>>

\begin{document}
% Remove at submission:
\slugcomment{{\color{red} \textbf{To appear on arXiv on 13 September 2016 (\difftoday{2016}{9}{7}away)}}}

@@

@@

\noindent{}where $\Lambda$ is a regularization parameter which we will heuristically set
for each model in later sections, and $Q(\vectheta)$ is a regularizing function that 
encourages $\vectheta$ values to take on zero values without breaking convexity:
\begin{eqnarray}\label{eq:regularization-function}
	Q(\vectheta) = \sum_{d=1}^{D-1} |{\theta_d}| \quad .
\end{eqnarray}

@@

The \rave\ survey performed repeat observations for 43,918 stars with time 
intervals ranging from a few hours to up to four years.  This timing was 
constructed to be quasi-logarithmic such that spectroscopic binaries could
be optimally identified. Most of the stars that were observed multiple times
were only observed twice, with thirteen visits being the maximum number 
of observations for any target.  These repeat observations allow us to 
quantify the level of (in)correctness in our formal errors.  For every star
with multiple visits we constructed a high S/N stacked spectrum for that
star, weighted by the inverse variances in the individual visit spectra,
which then served as the basis of comparison to all individual visits.  
Figure \ref{fig:formal-errors-comparison} shows the difference in labels 
between the comparison spectrum and a repeat visit, normalized by their 
formal errors summed in quadrature (e.g., 
$\Delta\logg/\sqrt{\sigma_{\logg,stacked}^2 + \sigma_{\logg,visit}^2}$).
If our measurements were unbiased by S/N and the errors were representative, 
these values should be normally distributed with a zero mean and unit variance.
\stub{Are they? Should we inflate our formal errors?}

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/ges-comparison.pdf}
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{Gaia-ESO Survey} fourth internal data release.\label{fig:ges-dr4-comparison}}
\end{figure*}
